ACNP 2024 MS ANXIETY

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t
```

@@

>>>>

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t

#looking at physical health and mental health in sick vs healthy

#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
physical_health_t_sick_vs_healthy

#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_health_t_sick_vs_healthy
```

@@

### do just with super sick and healthy
df_for_promis_plot_mental_vs_physical_healthy_no_summarize_just_sick_and_healthy <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  filter(anxiety_dose != 1) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  mutate(anxiety_dose = as.numeric(anxiety_dose)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score) %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI)

#aanxiety_dose                                       -1.0417     0.2611 24.3607  -3.989  0.00053 ***
##health_variablephysical_health_score                0.1875     0.2731 17.0000   0.687  0.50155    
#anxiety_dose:health_variablephysical_health_score   0.4063     0.2249 17.0000   1.806  0.08864 .  
anxiety_dose_by_health_var_score_just_sick_and_healthy <- lmer(PROMIS_Score ~anxiety_dose*health_variable + (1|EMPI), df_for_promis_plot_mental_vs_physical_healthy_no_summarize_just_sick_and_healthy)
summary(anxiety_dose_by_health_var_score_just_sick_and_healthy)
```
